% Family songbook
% TODO:
%  Improve line spacing
%  Change chord font
%  Increase font size
%  Make titles better
%  Try html export?
%  Add youtube links
%  Split songs apart into files? Might make it harder to do formatting specifics, but with needspace that's less of an issue
%  End or Outro?
%  

\documentclass[twocolumn,a4paper,twoside,11pt]{article}


\usepackage[
  inner=40pt,
  textwidth=480pt,
  top=1cm,
  bottom=2cm
]{geometry}

\usepackage{leadsheets}
\usepackage{array}
\usepackage{needspace} % allows conditional page breaks if not enough space left in page/column
\usepackage{xcolor}

\definesongproperty{suggestedby}

\definesongtitletemplate{custom}{
  \begin{tabular}{@{}l@{}}
    \hline \\[1pt]
    \bfseries\huge\songproperty{title} \\[-1pt]
    \ifsongproperty{composer} {\normalfont\small\sffamily{By \songproperty{composer}} \\}{}
    
    \ifsongproperty{suggestedby} { \normalfont\small\sffamily{Suggested by \songproperty{suggestedby}} \\} { \\[-15pt]}
    \\[-10pt]
  \end{tabular}
}

\newcommand{\formatChorusLabel}[1]{\colorbox{gray}{\textbf{\colorbox{white}{#1}} \hspace{-10pt}}}

\setleadsheets{
    title-template = custom,
    verse/numbered = true,
    % verse/label-format = \bfseries,
    chorus/label-format = \small\formatChorusLabel,
    % chorus/template = \songproperty{label},
    % bridge/label-format = \bfseries,
    % intro/label-format = \bfseries,
    % itemize/label-format = \bfseries,
    verses-label-format = \bfseries\small,
    align-chords = l,
    % text-format = {\fontsize{14pt}{15pt}},  % second dimension should be larger than the first!  
    chords/format = {\fontsize{12pt}{12pt}\color{blue}\bfseries\sffamily},
}

% \newcommand{\threesidebox}[1]{\fboxsep=0pt\fbox{\strut#1}\kern-\fboxrule}

% Custom command for chorus indication
\newcommand{\chorusref}[1]{\fbox{\textit{$\uparrow$ {#1}}}}



\begin{document}

\begin{song}{title={Banana Bread}, composer={Caspar Babypants, 2016}, suggestedby={Jim and Amanda Hays}}

\begin{chorus}
^{D}Banana bread, banana bread. \\
^{G}We can be ^{D}banana bread. \\
^{G}We're not pretty but we're not ^{A}dead... \\
^{Cadd2}{We can be} banana ^{D}bread!
\end{chorus}

\begin{verse}
^{G}You brought us home from the grocery. \\
We looked so snappy, \\
^{D}Put us on the counter top over there. \\
We were so happy. \\
Then ^{E7}you forgot about us, lunch after lunch. \\
^{A}Now we are a ^{A6}fruit fly covered, \\
^{A7}brown, and bummed out bunch, but
\end{verse}

\chorusref{Chorus}

\begin{verse}
^{G}Once upon a time \\
we were so yellow, \\
^{D}cheery, bright, and smiling, \\
a bunch of happy fellows. \\
Then ^{E7}we got forgotten. \\
Now it's almost too late. \\
^{A}but you can still make us into something \\
tasty to put on your plate.
\end{verse}

\chorusref{Chorus}

\needspace{2\baselineskip} % Don't let the bridge get broken across

\begin{bridge}
|: ^{G}(Ba - na - na) ^{E7}(ba - na - na) \\
^{Bm}(ba - na - na) ^{C}(Ba - na - na) :| \\
^{A}Ba - na - na - na -na -na - na na ^{Ab}
\end{bridge}

\begin{verse}
^{G}Me and the boys have been \\
together for so long. \\
^{D}We grew up on a banana tree. \\
and learned to sing this song. \\
^{E7}All the young bananas learned it. \\
in case they get forgotten \\
^{A}So people don't throw them out \\
just because they look a little bit rotten.
\end{verse}

\chorusref{Chorus}

\begin{outro}
|: ^{Cadd2}{We can be} banana ^{D}bread! :| (x3)
\end{outro}

\end{song}

\begin{song}{title={You fill up my senses}, composer={John Denver, 1974}, key=D}
\begin{verse}
^{D}You ^{Dsus4}{fill up my} ^*{G}sen ^{A}ses ^{Bm} \\
like a ^{G}night in a ^{D}forest, ^{D/C#} ^{Bm} \\
like the ^{A}mountains in ^*{G}spring ^{F#m}time, ^{Em} \\
like a ^{G}walk in the ^{A7}rain, \\
like a storm in the ^*{G}de ^{A}sert ^{Bm} \\
like a ^{G}sleepy blue ^{D}ocean. ^{D/C#} ^{Bm} \\
You ^{A}fill up my ^*{G}sen ^{F#m}ses ^{Em} \\
come ^{A7}fill me a^{D}gain. ^{Dsus4}
\end{verse}
\begin{verse}
^{D} ^{Dsus4}{Come let me} ^{G}love ^{A}you, ^{Bm} \\
let me ^{G}give my life ^{D}to you. ^{D/C#} ^{Bm} \\
Let me ^{A}drown in your ^*{G}laugh ^{F#m}ter, ^{Em} \\
let me ^{G}die in your ^{A7}arms. \\
Let me lay down be^{G}side ^{A}you. ^{Bm} \\
Let me ^{G}always be ^{D}with you. ^{D/C#} ^{Bm} \\
^{A}Come let me ^{G}love ^{F#m}you, ^{Em} \\
come ^{A7}love me a^{D}gain. ^{Dsus4} ^{D}
\end{verse}

\chorusref{Verse 1}
\end{song}


\needspace{8\baselineskip} % Don't start new song toward end of column
\begin{song}{title={Country roads}, composer={John Denver}, key=G}
\begin{verse}
^{G}{\: Almost} Heaven^{Em}{; West} Virginia^{D}, \\
Blue Ridge Mountains, ^{C}Shenandoah ^{G}River. \\
^{G}{\: Life} is old there, ^{Em}older than the trees, \\
^{D}younger than the the mountains, \\
^{C}blowin' like a ^{G}breeze.
\end{verse}
\begin{chorus}
Country ^{G}roads, take me ^{D}home, \\
to the ^{Em}place, I be^{C}long, \\
West Virg^{G}inia, mountain ^{D}mama, \\
take me ^{C}home, country ^{G}roads.
\end{chorus}

\begin{verse}
^{G}{\: All my} memories^{Em}{\: gather} round her: \\
^{D}{\: miner's} lady, ^{C}stranger  to blue wa^{G}ter, \\
^{G}{\: dark} and dusty, ^{Em}painted on the sky; \\
^{D}misty taste of moonshine; \\
^{C}teardrop in my ^{G}eye.
\end{verse}

\chorusref{Chorus}

\begin{bridge}
^{Em}{I hear} her ^{D}voice in the ^{G}morning hour she calls me. \\
The ^{C}radio re^{G}minds me of my ^{D}home far away. \\
And ^{Em}driving down the ^{F}road I get a ^{C}feeling \\
that I ^{G}should have been home ^{D}yesterday, yester^{D7}day.
\end{bridge}

\chorusref{Chorus}

\begin{outro}
|: Take me ho^{D}me, down country r^{G}oads. :|
\end{outro}

\end{song}

\needspace{8\baselineskip} % Don't start new song toward end of column
\begin{song}{title={The parting glass}, composer={The Wailin' Jennys, 2004}, key=G}
\begin{verse}
Oh ^{Em}{all the} ^{Cadd2}money that ^{G}e'er I ^{D}spent \\
I ^{G}spent it in good company. ^{D} \\
And ^{Em}{all the} ^{Cadd2}harm that ^{G}e'er I've ^{D}done, \\
^{G/D}{alas, it} ^{G}was to ^{Em}none but ^{C}me. \\
\\
And ^{G}all I've done for want of wit, \\
to ^{Am}memory ^{D}now, I ^{G}can't re^{D}call. \\
So ^{Em}fill to ^{C}me the ^{G}parting ^{D}glass. \\
^{G/D}Goodnight and ^{G}joy be ^{Em}with you ^{C}all. \\
\end{verse}

\begin{verse}
Oh ^{Em}{all the} ^{Cadd2}comrades that ^{G}e'er I've ^{D}had \\
are ^{G}sorry for my going away. ^{D} \\
And ^{Em}{all the} ^{Cadd2}sweethearts that ^{G}e'er I've ^{D}had, \\
^{G/D}{would wish} me ^{G}one more ^{Em}day to ^{C}stay. \\
\\
But ^{G}since it falls unto my lot, \\
that ^{Am}{I should} ^{D}rise and ^{G}you should ^{D}not, \\
I'll ^{Em}gently ^{C}rise and I'll ^{G}softly ^{D}call \\
^{G/D}Goodnight and ^{G}joy be ^{Em}with you ^{C}all. \\
\end{verse}
\begin{outro}[name={End}, named=true]
^{G/D}Goodnight and ^{G}joy be with you ^{Em}all. \\
\end{outro}

\end{song}

\needspace{10\baselineskip} % Don't start new song toward end of column
\begin{song}{title={His cheeseburger}, composer={Veggietales, 1998}, key=A}

\begin{verse}
He ^{A}said to her, ``I'd like a cheese^{E}burger \\
and I ^{G}might like a milkshake as ^{D}well." \\
She ^{A}said to him, ``I can't get you ^{E}either." \\
And he ^{G}said, ``Isn't this Burger ^{D}Bell?" \\
\\
She ^{C#}said, ``Yes, it is, but we're ^{F#m}closed now, \\
but we ^{D}open tomorrow at ^{E}ten." \\
He ^{F#m}said, "I am extremely ^{E}hungry, \\
But I ^{D}guess I can wait until ^{E}then!" ^{E7}
\end{verse}

\begin{chorus}
'Cause ^{E7}you're his ^*{A}{cheeseburg} ^{E7}{er}, \\
his yummy ^*{A}{cheeseburg} ^{E7}{er}. \\
He'll wait for ^{Bm7}you, ya \\
he'll wait for ^{E7}you. \\
Oh, you are his ^*{A}{cheeseburg} ^{E7}{er}, \\
his tasty ^*{A}{cheeseburg} ^{E7}{er}. \\
He'll wait for ^{Bm7}you, \\
oh he will wait for ^{E7}you. \\
\end{chorus}

\begin{verse}
He ^{A}stayed at the drive-thru till ^{E}sunrise, \\
(He ^{G}may have dozed off once or ^{D}twice) \\
when he ^{A}spotted a billboard for ^{E}Denny's: \\
^{G}"Bacon and eggs for half ^{D}price." \\
\\
How ^{C#}could he resist such an ^{F#m}offer? \\
He ^{D}really needed something to ^{E}munch. \\
^{F#m}Cheeseburger, please do not get ^{E}angry! \\
He'll ^{D}eat and be back here for ^{E}lunch. ^{E7}
\end{verse}

\begin{chorus}
'Cause ^{E7}you're his ^*{A}{cheeseburg} ^{E7}{er}, \\
his precious ^*{A}{cheeseburg} ^{E7}{er}. \\
Be back for ^{Bm7}you, \\
he'll be back for ^{E7}you. \\
Won't be so long ^*{A}{cheeseburg} ^{E7}{er}, \\
oh lovely ^*{A}{cheeseburg} ^{E7}{er}. \\
Be back for ^{Bm7}you. \\
Oh, ^{E}he'll be back for ^{A}you. ^{C#sus} ^{C#7}\\
\end{chorus}

\begin{bridge}
'Cause he ^{F#m}loves you cheeseburger with all his heart,
and there aint nothin' gonna tear you two apart. \\
And if the ^{E}world suddenly ran out of cheese \\
he would ^{C}get down on his hands and knees \\
to see if ^{Ab}someone accidentally \\
dropped some ^{C}cheese in the dirt, \\
and he would ^{D}wash it off for you, \\
^{D}wipe it off for you, \\
^{D}clean that dirty cheese off just for you!
\end{bridge}

\begin{outro}
^{NC}You are his cheeseburger. \: \: ^{G}
\end{outro}
\end{song}

\needspace{10\baselineskip} % Don't start new song toward end of column
\begin{song}{title={Hallelujah}, composer={Leonard Cohen, 1984}, key=C}
\begin{verse}
I've ^{A}heard there was a ^{F#m}secret chord \\
that ^{A}David played and it ^{F#m}pleased the Lord, \\
but ^{D}you don't really ^{E}care for music, ^{A}do ya?^{E} \\
It ^{A}goes like this: the ^{D}4th, the ^{E}5th, \\
the ^{F#m}minor fall, the ^{D}major lift. \\
The ^{E}baffled king com^{C#7}posing Halle^{F#m}lujah. \\
\end{verse}

\begin{chorus}
Halle^{D}lujah, Halle^{F#m7}lujah, \\
Halle^{D}lujah, Halle^{A}lu - ^{E}u - ^{A}jah. ^{E}
\end{chorus}

\begin{verse}
^{\bfseries{$\uparrow$}}Your faith was strong, but you needed proof. \\
You saw her bathing on the roof. \\
Her beauty in the moonlight overthrew ya. \\
She tied you to a kitchen chair, \\
she broke your throne, and she cut your hair, \\
and from your lips she drew the Hallelujah. \\[-15pt]
\end{verse}
% \chorusref{Chorus}

\begin{verse}
Baby, I've been here before, \\
I know this room, I walked this floor. \\
I used to live alone before I knew ya. \\
I've seen your flag on the marble arch, \\
but love is not a victory march, \\
it's a cold and it's a broken Hallelujah. \\[-15pt]
\end{verse}
% \chorusref{Chorus}

\begin{verse}
Maybe there's a God above, \\
but all I've ever learned from love was \\
how to shoot at someone who outdrew ya. \\
It's not a cry you can hear at night, \\
it's not somebody who has seen the light, \\
it's a cold and it's a broken Hallelujah. \\[-15pt]
\end{verse}
% \chorusref{Chorus}

\begin{verse}
You say I took the name in vain, \\
but I don't even know the name, \\
and if I did, well really, what's it to ya? \\
There's a blaze of light in every word. \\
It doesn't matter which you heard, \\
the holy or the broken Hallelujah. \\[-15pt]
\end{verse}
% \chorusref{Chorus}

\begin{verse}
I did my best, it wasn't much. \\
I couldn't feel, so I tried to touch. \\
I've told the truth. I didn't come to fool ya. \\
And even though it all went wrong, \\
I'll stand before the Lord of Song \\
with nothing on my tongue but Hallelujah \\[-15pt]
\end{verse}
\begin{outro}
|: Halle^{D}lujah, Halle^{F#m7}lujah, \\
Halle^{D}lujah, Halle^{A}lu - ^*{E}jah. :| {x3} \\
Halle^{D}lujah, Halle^{F#m7}lujah, \\
Halle^{D}lujah, Halle^{A}lu - ^{E}u - ^{A}jah.
\end{outro}
\end{song}

\needspace{10\baselineskip} % Don't start new song toward end of column
\begin{song}{title={Here comes the sun}, composer={The Beatles, 1969}, key=D}

\begin{chorus}
^{D} Here comes the sun. (doo doo doo doo) \\
^{G} Here comes the ^{E7}sun, \& I say^{D} it's alright.
\end{chorus}

\begin{verse}
^{D}Little darling, it's been a \\
^{G}long, cold, lonely ^{A7}winter. \\
^{D}Little darling, it feels like \\
^{G}years since it's been ^{A7}here. \\
\end{verse}
\chorusref{Chorus}

\begin{verse}
^{$\uparrow$}Little darling, the smile's \\
returning to their faces. \\
Little darling, it seems like \\
years since it's been here. \\
\end{verse}
\chorusref{Chorus}

\begin{bridge}
|: ^{F}Sun, ^{C}sun, ^{G}sun, here it ^{D}comes. :| (x5) \\[10pt]
^{A7} ^{A7sus} ^{A7} \\[-15pt]
\end{bridge}

\begin{verse}
^{$\uparrow$}Little darling, I feel the \\
ice is slowly melting. \\
Little darling, it seems like \\
years since it's been clear. \\
\end{verse}

\chorusref{Chorus} (x2)

\begin{outro}
^{D} It's alright.
\end{outro}
\end{song}

\needspace{10\baselineskip} % Don't start new song toward end of column
\begin{song}{title={Imagine}, composer={John Lennon, 1971}, key=C}
\begin{intro}
|: \writechord{C} \: \writechord{Cmaj7} \: | \: \writechord{F} :|
\end{intro}
\begin{verse}
^{C} Imagine there^{Cmaj7}{'s no} ^{F}heaven. \\
^{C} It's easy i^*{Cmaj7}{f you} ^{F}try. \\
^{C} No hell ^{Cmaj7}below ^{F}us. \\
^{C} Above u^{Cmaj7}{s only} ^{F}sky. \\
\\
^{F} Imagine ^{Am}all the ^{Dm7}people ^{F/C} \\
^{G}living for ^*{C}to ^{G7}day. (ah - ha - ahh)
\end{verse}
\begin{verse}
^{$\uparrow$}Imagine there's no countries. \\
It isn't hard to do. \\
Nothing to kill or die for, \\
and no religion, too. \\[5pt]
Imagine all the people \\
living life in peace. (you - hoo - hooo) \\
\end{verse}
\begin{chorus}
^{F} You may ^{G}say I'm a ^{C}dreamer, \: ^{Cmaj7} ^{E7} \\
^{F} but I'm ^{G}not the only ^{C}one. \: ^{Cmaj7} ^{E7} \\
^{F} I hope some^{G}day you'll ^{C}join us, ^{Cmaj7} ^{E7} \\
^{F} and the ^{G}world will ^{C}be as one. \\
\end{chorus}
\begin{verse}
Imagine no possessions. \\
I wonder if you can. \\
No need for greed or hunger, \\
a brotherhood of man. \\[5pt]
Imagine all the people \\
sharing all the world. (you - hoo - hooo) \\
\end{verse}
\chorusref{Chorus}
\end{song}

\needspace{10\baselineskip} % Don't start new song toward end of column
\begin{song}{title={Alleluia, the Great Storm}, composer={Bob Franke, 1982}, key=D}
\begin{chorus}
|: ^{G}Alleluia, the ^{D}Great Storm is ^{Em}over, \\
lift ^{G}up your ^{C}wings and ^{D}fly. :|
\end{chorus}

\begin{verse}
The ^{G}thunder and lightning \\
gave ^{C}voice to the ^{G}night, \\
the ^{C}little ^{D}lame ^{G}child \\
cried a^{C}loud in her ^{G}fright. \\
^{G}Hush, little baby, a ^{C}story I'll ^{G}tell \\
of a ^{C}love ^{D}that has ^{Em}vanquished \\
the ^{C}powers of ^{D}hell.
\end{verse}
\chorusref{Chorus}
\begin{verse}
^{$\uparrow$}Sweetness in the air, \& justice on the wind, \\
laughter in the house \\
where the mourners had been. \\
The deaf shall have music, \\
the blind have new eyes, \\
the standards of death \\
taken down by surprise.
\end{verse}
\chorusref{Chorus}
\begin{verse}
Release for the captives, \& end to the wars, \\
new streams in the desert, \\
new hope for the poor. \\
The little lame children \\
will dance as they sing, \\
and play with the bears \\
and the lions in spring.
\end{verse}
\chorusref{Chorus}
\begin{verse}
Hush little baby, let go of your fear. \\
The Lord loves his own \\
and your mother is here. \\
The child fell asleep as the lantern did burn, \\
the mother sang on \\
till her bridegroom's return.
\end{verse}
\chorusref{Chorus}
\end{song}

\needspace{10\baselineskip} % Don't start new song toward end of column
\begin{song}{title={You'll be back}, composer={Lin‐Manuel Miranda, 2021}, key=G}
\begin{intro}
\writechord{G} \writechord{G7} \writechord{C} \writechord{Am7} \writechord{D}
\end{intro}
\begin{verse}
You ^{G}say: The price of my love's \\
not a ^{C}price that you're willing to ^{Am7}pay. ^{D} \\
You ^{G}cry in your tea which you hurl \\
in the ^{C}sea when you see me go ^{Am7}by. \\
^{D}Why so ^{Em}sad? Re^{D}member  we made an \\
ar^{C}rangement when you went a^{Am7}way. \\
Now you're ^{D}making me ^{Em}mad. \\
Re^{D}member despite our es^{C}trangement, \\
I'm your ^{D}man.
\end{verse}

\begin{chorus}
You'll be ^{G}back, soon you'll ^{G7}see. \\
You'll re^{C}member you belong to ^{Am7}me. \\
^{D}You'll be ^{G}back, time will ^{G7}tell. \\
You'll re^{C}member that I served you ^{Am7}well. \\
^{D}Oceans ^{Em}rise, empires ^{G}fall, \\
we have ^{C}seen each other through it ^{Cm}all, \\
and when ^{Em}push comes to ^{G}shove, \\[10pt]
I will ^{C}send a fully armed bat^{Am7}talion \\
to re^{D}mind you of my ^{G}love!
\end{chorus}

\begin{bridge}[name={Da Dats}, named=true]
^{G}Da da da dat ^{G7}daa! Dat da da da ^{C}daaya da, \\
da da ^{Cm}dat dat daaya ^{G}da. \\
Da da da dat ^{G7}daa! Dat da da da ^{C}daaya da, \\
da da ^{Cm}dat dat daa... \\
\end{bridge}

\begin{verse}
You ^{Em}say: Our love is  draining \\
and you can't go ^{C}on\_\_\_\_\_! ^{Cm} \\
You'll ^{Em}{be the} one com^{G}plaining \\
when I am ^*{C}go\_\_\_\_\_ ^{Cm}ne! \\
\\
\textbf{AND} ^{Am7}{\textbf{NO! Don't change the}} ^{D7}{\textbf{subject!}} \\
'Cause ^{Am7}you're my favorite ^{D7}subject. \\
My ^{F}sweet, submissive ^{C}subject. \\
My ^{F}loyal, royal ^{C}subject, \\
for^{G}ever, \& ^{G7}ever, \& ^{Cm}ever, \& ever, \& ever...
\end{verse}

\begin{chorus}
^{$\uparrow$}You'll be back, like before, \\
I will fight the fight and win the war, \\
for your love, for your praise. \\
And I'll love ya 'til my dying days. \\
When you're gone, I'll go mad, \\
so don't throw away this thing we had, \\
'cause when push comes to shove, \\
I will kill your friends and family... \\
to remind you of my love!
\end{chorus}

\chorusref{Da Dats} (x2)
\end{song}

\end{document}
