\begin{song}{title={Banana Bread}, composer={Caspar Babypants, 2016}, suggestedby={Jim and Amanda Hays}}

\begin{chorus}
^{D}Banana bread, banana bread. \\
^{G}We can be ^{D}banana bread. \\
^{G}We're not pretty but we're not ^{A}dead... \\
^{Cadd2}{We can be} banana ^{D}bread!
\end{chorus}

\begin{verse}
^{G}You brought us home from the grocery. \\
We looked so snappy, \\
^{D}Put us on the counter top over there. \\
We were so happy. \\
Then ^{E7}you forgot about us, lunch after lunch. \\
^{A}Now we are a ^{A6}fruit fly covered, \\
^{A7}brown, and bummed out bunch, but
\end{verse}

\chorusref{Chorus}

\begin{verse}
^{G}Once upon a time \\
we were so yellow, \\
^{D}cheery, bright, and smiling, \\
a bunch of happy fellows. \\
Then ^{E7}we got forgotten. \\
Now it's almost too late. \\
^{A}but you can still make us into something \\
tasty to put on your plate.
\end{verse}

\chorusref{Chorus}

\needspace{2\baselineskip} % Don't let the bridge get broken across

\begin{bridge}
|: ^{G}(Ba - na - na) ^{E7}(ba - na - na) \\
^{Bm}(ba - na - na) ^{C}(Ba - na - na) :| \\
^{A}Ba - na - na - na -na -na - na na ^{Ab}
\end{bridge}

\begin{verse}
^{G}Me and the boys have been \\
together for so long. \\
^{D}We grew up on a banana tree. \\
and learned to sing this song. \\
^{E7}All the young bananas learned it. \\
in case they get forgotten \\
^{A}So people don't throw them out \\
just because they look a little bit rotten.
\end{verse}

\chorusref{Chorus}

\begin{outro}
|: ^{Cadd2}{We can be} banana ^{D}bread! :| (x3)
\end{outro}

\end{song}
