\begin{song}{title={Hallelujah}, composer={Leonard Cohen, 1984}, key=C}

\begin{verse}
I've ^{A}heard there was a ^{F#m}secret chord \\
that ^{A}David played and it ^{F#m}pleased the Lord, \\
but ^{D}you don't really ^{E}care for music, ^{A}do ya?^{E} \\
It ^{A}goes like this: the ^{D}4th, the ^{E}5th, \\
the ^{F#m}minor fall, the ^{D}major lift. \\
The ^{E}baffled king com^{C#7}posing Halle^{F#m}lujah. \\
\end{verse}

\begin{chorus}
Halle^{D}lujah, Halle^{F#m7}lujah, \\
Halle^{D}lujah, Halle^{A}lu - ^{E}u - ^{A}jah. ^{E}
\end{chorus}

\begin{verse}
^{\bfseries{$\uparrow$}}Your faith was strong, but you needed proof. \\
You saw her bathing on the roof. \\
Her beauty in the moonlight overthrew ya. \\
She tied you to a kitchen chair, \\
she broke your throne, and she cut your hair, \\
and from your lips she drew the Hallelujah. \\[-15pt]
\end{verse}
% \chorusref{Chorus}

\begin{verse}
Baby, I've been here before, \\
I know this room, I walked this floor. \\
I used to live alone before I knew ya. \\
I've seen your flag on the marble arch, \\
but love is not a victory march, \\
it's a cold and it's a broken Hallelujah. \\[-15pt]
\end{verse}
% \chorusref{Chorus}

\begin{verse}
Maybe there's a God above, \\
but all I've ever learned from love was \\
how to shoot at someone who outdrew ya. \\
It's not a cry you can hear at night, \\
it's not somebody who has seen the light, \\
it's a cold and it's a broken Hallelujah. \\[-15pt]
\end{verse}
% \chorusref{Chorus}

\begin{verse}
You say I took the name in vain, \\
but I don't even know the name, \\
and if I did, well really, what's it to ya? \\
There's a blaze of light in every word. \\
It doesn't matter which you heard, \\
the holy or the broken Hallelujah. \\[-15pt]
\end{verse}
% \chorusref{Chorus}

\begin{verse}
I did my best, it wasn't much. \\
I couldn't feel, so I tried to touch. \\
I've told the truth. I didn't come to fool ya. \\
And even though it all went wrong, \\
I'll stand before the Lord of Song \\
with nothing on my tongue but Hallelujah \\[-15pt]
\end{verse}

\begin{outro}
|: Halle^{D}lujah, Halle^{F#m7}lujah, \\
Halle^{D}lujah, Halle^{A}lu - ^*{E}jah. :| {x3} \\
Halle^{D}lujah, Halle^{F#m7}lujah, \\
Halle^{D}lujah, Halle^{A}lu - ^{E}u - ^{A}jah.
\end{outro}

\end{song}
