\begin{song}{title={His cheeseburger}, composer={Veggietales, 1998}, key=A}

\begin{verse}
He ^{A}said to her, ``I'd like a cheese^{E}burger \\
and I ^{G}might like a milkshake as ^{D}well." \\
She ^{A}said to him, ``I can't get you ^{E}either." \\
And he ^{G}said, ``Isn't this Burger ^{D}Bell?" \\
\\
She ^{C#}said, ``Yes, it is, but we're ^{F#m}closed now, \\
but we ^{D}open tomorrow at ^{E}ten." \\
He ^{F#m}said, "I am extremely ^{E}hungry, \\
But I ^{D}guess I can wait until ^{E}then!" ^{E7}
\end{verse}

\begin{chorus}
'Cause ^{E7}you're his ^*{A}{cheeseburg} ^{E7}{er}, \\
his yummy ^*{A}{cheeseburg} ^{E7}{er}. \\
He'll wait for ^{Bm7}you, ya \\
he'll wait for ^{E7}you. \\
Oh, you are his ^*{A}{cheeseburg} ^{E7}{er}, \\
his tasty ^*{A}{cheeseburg} ^{E7}{er}. \\
He'll wait for ^{Bm7}you, \\
oh he will wait for ^{E7}you. \\
\end{chorus}

\begin{verse}
He ^{A}stayed at the drive-thru till ^{E}sunrise, \\
(He ^{G}may have dozed off once or ^{D}twice) \\
when he ^{A}spotted a billboard for ^{E}Denny's: \\
^{G}"Bacon and eggs for half ^{D}price." \\
\\
How ^{C#}could he resist such an ^{F#m}offer? \\
He ^{D}really needed something to ^{E}munch. \\
^{F#m}Cheeseburger, please do not get ^{E}angry! \\
He'll ^{D}eat and be back here for ^{E}lunch. ^{E7}
\end{verse}

\begin{chorus}
'Cause ^{E7}you're his ^*{A}{cheeseburg} ^{E7}{er}, \\
his precious ^*{A}{cheeseburg} ^{E7}{er}. \\
Be back for ^{Bm7}you, \\
he'll be back for ^{E7}you. \\
Won't be so long ^*{A}{cheeseburg} ^{E7}{er}, \\
oh lovely ^*{A}{cheeseburg} ^{E7}{er}. \\
Be back for ^{Bm7}you. \\
Oh, ^{E}he'll be back for ^{A}you. ^{C#sus} ^{C#7}\\
\end{chorus}

\begin{bridge}
'Cause he ^{F#m}loves you cheeseburger with all his heart,
and there aint nothin' gonna tear you two apart. \\
And if the ^{E}world suddenly ran out of cheese \\
he would ^{C}get down on his hands and knees \\
to see if ^{Ab}someone accidentally \\
dropped some ^{C}cheese in the dirt, \\
and he would ^{D}wash it off for you, \\
^{D}wipe it off for you, \\
^{D}clean that dirty cheese off just for you!
\end{bridge}

\begin{outro}
^{NC}You are his cheeseburger. \: \: ^{G}
\end{outro}
\end{song}
