\begin{song}{title={You'll be back}, composer={Lin‐Manuel Miranda, 2021}, key=G}

\begin{intro}
\writechord{G} \writechord{G7} \writechord{C} \writechord{Am7} \writechord{D}
\end{intro}

\begin{verse}
You ^{G}say: The price of my love's \\
not a ^{C}price that you're willing to ^{Am7}pay. ^{D} \\
You ^{G}cry in your tea which you hurl \\
in the ^{C}sea when you see me go ^{Am7}by. \\
^{D}Why so ^{Em}sad? Re^{D}member  we made an \\
ar^{C}rangement when you went a^{Am7}way. \\
Now you're ^{D}making me ^{Em}mad. \\
Re^{D}member despite our es^{C}trangement, \\
I'm your ^{D}man.
\end{verse}

\begin{chorus}
You'll be ^{G}back, soon you'll ^{G7}see. \\
You'll re^{C}member you belong to ^{Am7}me. \\
^{D}You'll be ^{G}back, time will ^{G7}tell. \\
You'll re^{C}member that I served you ^{Am7}well. \\
^{D}Oceans ^{Em}rise, empires ^{G}fall, \\
we have ^{C}seen each other through it ^{Cm}all, \\
and when ^{Em}push comes to ^{G}shove, \\[10pt]
I will ^{C}send a fully armed bat^{Am7}talion \\
to re^{D}mind you of my ^{G}love!
\end{chorus}

\begin{bridge}[name={Da Dats}, named=true]
^{G}Da da da dat ^{G7}daa! Dat da da da ^{C}daaya da, \\
da da ^{Cm}dat dat daaya ^{G}da. \\
Da da da dat ^{G7}daa! Dat da da da ^{C}daaya da, \\
da da ^{Cm}dat dat daa... \\
\end{bridge}

\begin{verse}
You ^{Em}say: Our love is  draining \\
and you can't go ^{C}on\_\_\_\_\_! ^{Cm} \\
You'll ^{Em}{be the} one com^{G}plaining \\
when I am ^*{C}go\_\_\_\_\_ ^{Cm}ne! \\
\\
\textbf{AND} ^{Am7}{\textbf{NO! Don't change the}} ^{D7}{\textbf{subject!}} \\
'Cause ^{Am7}you're my favorite ^{D7}subject. \\
My ^{F}sweet, submissive ^{C}subject. \\
My ^{F}loyal, royal ^{C}subject, \\
for^{G}ever, \& ^{G7}ever, \& ^{Cm}ever, \& ever, \& ever...
\end{verse}

\begin{chorus}
^{$\uparrow$}You'll be back, like before, \\
I will fight the fight and win the war, \\
for your love, for your praise. \\
And I'll love ya 'til my dying days. \\
When you're gone, I'll go mad, \\
so don't throw away this thing we had, \\
'cause when push comes to shove, \\
I will kill your friends and family... \\
to remind you of my love!
\end{chorus}

\chorusref{Da Dats} (x2)

\end{song}
